Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-25 prop_letter.tex
prop_letter.tex Fix typo...

\yutsung{Even if we have expectation value of an observable, I don't
know how to reason Mermin square~(\ref{eq:MerminSquare}) directly
with quantum IVPM so far. The problem is the valuation function~$v$
is not an expectation value. Since $E\left[XY\right]=E\left[X\right]E\left[Y\right]$,
corresponding to Eq.~(\ref{eq:deterministic-product}), doesn't hold
for expectation value except $X$ and $Y$ are uncorrelated or even
independent~\cite{rohatgi2011introduction}.}

>>>>

\yutsung{Even if we have expectation value of an observable, I don't
know how to reason Mermin square~(\ref{eq:MerminSquare}) directly
with quantum IVPM so far. The problem is the valuation function~$v$
is not an expectation value. Since $E\left[XY\right]=E\left[X\right]E\left[Y\right]$,
corresponding to Eq.~(\ref{eq:deterministic-product}), doesn't hold
for expectation value except $X$ and $Y$ are uncorrelated or even
independent~\cite{rohatgi2011introduction}.

I think the real question is: Can we use the expectation value and
Mermin square to simplify the proof that there is no $\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $?}
